---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rworkshoppackage

<!-- badges: start -->
<!-- badges: end -->

The goal of rworkshoppackage is to showcase as a demo at the Pune RUG meetup.

## Installation

You can install the development version of rworkshoppackage like so:

## ⬇️ Installing `rworkshoppackage`

Install the `pak` package. Y
You can install the development version of `rworkshoppackage` from [GitHub](https://github.com/) with

```{r, echo = TRUE}  
# install.packages("pak")  
pak::pak("jyoti-bhogal/rworkshoppackage-public")  
```  





## Usage

Multiply 21 by 48

This is a basic example which shows you how to solve a common problem:


```r
library(rworkshoppackage)
a <- 21
b <- 48
c <- rworkshoppackage::multiply(a,b)
print(c)
```

You can also embed plots. For example:

```{r pressure, echo = FALSE}
#plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
